Hemispheric Lateralization and Outcomes After ICH: A Pooled Analysis of Clinical Trials

### 2023-01-18 data-wrangling.qmd
writing to csv
html updates
updates

library(tidyverse)
library(tableone)
library(data.table)
library(haven) # Importing SAS Files
library(janitor)
library(lubridate)
library(readxl)

@@

@@

>>>>

library(tidyverse)
library(tableone)
library(data.table)
library(haven) # Importing SAS Files
library(janitor)
library(lubridate)
library(readxl)
library(Hmisc)

@@

ninds.combined$comfort.day <- round(ninds.combined$comfort.day)

@@

```{r output = TRUE}

write.csv(ninds.combined, file = "nindsCombined.csv")
